Text embedding models reveal high resolution insights into conceptual knowledge from short multiple choice quizzes

### 2023-01-27 paper/main.tex
backing up progress on discussion section-- mostly added a bunch of references

\textbf{JRM NOTE: add overview of our findings.  Also need (lots of) citations below...}

Teaching, like effective writing and speaking, is fundamentally about empathy.
Great teachers consider students' interests, backgrounds, and working memory
capacities, and flexibly optimize their teaching strategies within those
constraints. In the classroom, empathizing with students also means maintaining
open lines of communication by fostering an environment in which all students
feel comfortable speaking up if they have an exciting new idea, or if they are
having trouble understanding something. In-person instruction also often
entails dynamic student-teacher and student-student interactions. These
in-person interactions can provide the instructor with valuable information
about students' understanding of the course material, beyond what they can
glean solely from exams or assignments. In turn, this can allow the instructor
to adapt their teaching approaches on-the-fly according to students' questions
and behaviors. But what does great teaching look like in asynchronous online
courses, when the instructor typically prepares course lectures and materials
without knowing who will ultimately be learning from them? Can the empathetic
side of teaching be automated and scaled?

The notion of empathy is tightly associated with ``theory of mind'' of other
individuals. Considering others' unique perspectives, prior experiences,
knowledge, goals, etc., can help us to more effectively interact and
communicate. The knowledge and learning maps we estimate in our study
(Fig.~\ref{fig:knowledge-maps}) hint at one potential form that an automated
empathetic teacher might take. We imagine that automated content delivery
systems that \textbf{JRM NOTE: CONTINUE....}

@@

Alongside these questions, there is a growing desire to extend existing
theories beyond the domain of lab testing rooms and into real classrooms. In
part, this has led to a recent resurgence of ``naturalistic'' or
``observational'' experimental paradigms that attempt to better reflect more
ethologically valid phenomena that are more directly relevant to real-world
situations and behaviors. In turn, this has brought new challenges in data
analysis and interpretation. A key step towards solving these challenges will
be to build explicit models of real-world scenarios and how people behave in
them (e.g., models of how people learn conceptual content from real-world
courses, as in our current study). A second key step will be to understand
which sorts of signals derived from behaviors and/or other measurements (e.g.,
neurophysiological data; \textbf{CITE Hassan/Norman lab stuff, Poeppel lab
stuff, Para lab stuff, etc.}) might help to inform these models. A third major
step will be to develop and employ reliable ways of evaluating the complex
models and data that are a hallmark of naturalistic paradigms.

>>>>

Teaching, like effective writing and speaking, is fundamentally about
empathy~\citep{AldrEtal22, StojEtal12, MeyeEtal19}. Great teachers consider
students' interests~\citep{SwarEtal12, Clar10}, backgrounds~\citep{MuijReyn10,
Rose76, denBEtal10}, and working memory capacities~\citep{Allo12}, and flexibly
optimize their teaching strategies within those constraints~\citep{GoodEtal07,
AndeEtal21, John02}. In the classroom, empathizing with students also means
maintaining open lines of communication~\citep{WulfWulf10} by fostering an
environment in which all students feel comfortable speaking up if they have an
exciting new idea, or if they are having trouble understanding
something~\citep{TurnBrai15, GarrRasm14}. In-person instruction also often
entails dynamic student-teacher and student-student interactions. These
in-person interactions can provide the instructor with valuable information
about students' understanding of the course material, beyond what they can
glean solely from exams or assignments~\citep{Engl09, vandEtal10c, HallWals02}.
In turn, this can allow the instructor to adapt their teaching approaches
on-the-fly according to students' questions and behaviors. But what does great
teaching look like in asynchronous online courses, when the instructor
typically prepares course lectures and materials without knowing who will
ultimately be learning from them? Can the empathetic side of teaching be
automated and scaled?

The notion of empathy also related to ``theory of mind'' of other
individuals~\citep{GoldWinn12, KansEtal15, Melt11}. Considering others' unique
perspectives, prior experiences, knowledge, goals, etc., can help us to more
effectively interact and communicate~\citep{ShaoEtal18, StepBaer06, Ratk18}.
The knowledge and learning maps we estimate in our study
(Fig.~\ref{fig:knowledge-maps}) hint at one potential form that an automated
``empathetic'' teacher might take. We imagine that automated content delivery
systems that adapt lessons on the fly according to continually updated
estimates of what students know and how quickly they are learning different
conceptual content~\citep[e.g., building on ideas such as ][and
others]{AndeSkwa86, Half88, Kuma05, WolzEtal88}.

@@

Alongside these questions, there is a growing desire to extend existing
theories beyond the domain of lab testing rooms and into real classrooms. In
part, this has led to a recent resurgence of ``naturalistic'' or
``observational'' experimental paradigms that attempt to better reflect more
ethologically valid phenomena that are more directly relevant to real-world
situations and behaviors. In turn, this has brought new challenges in data
analysis and interpretation. A key step towards solving these challenges will
be to build explicit models of real-world scenarios and how people behave in
them (e.g., models of how people learn conceptual content from real-world
courses, as in our current study). A second key step will be to understand
which sorts of signals derived from behaviors and/or other
measurements~\citep[e.g., neurophysiological data; ][]{NguyEtal22, MeshEtal20,
PoulEtal17, BeviEtal19, DikkEtal17} might help to inform these models. A third
major step will be to develop and employ reliable ways of evaluating the
complex models and data that are a hallmark of naturalistic paradigms.
